Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-06-01 manuscript.Rmd
Edits to methods

The social cohesion calculation was performed on the tweet corpus
containing (recalculate with new date span) English and (recalculate with
new date span) Arabic tweets. All hashtags and URLs were included in the
analysis.

@@

#### Metrics
While visual inspections can be informative, we can derive a variety of 
quantitative metrics from the cross-recurrence plot. Each of these metrics
provides information into the pattern and dynamics of the new shared system
between the original time series. These metrics are also critical for inferential
statistics. We will focus most directly on two of these metrics: 
*recurrence rate* and *determinism*.

@@

A number of other metrics provide insight not only into the amount of structure
between the systems but about the nature of this shared structure.
The average length of the line structures is called *mean line* (L), which can
be conceptualized as the average amount of time that the two time series move
together before one or both shift states. The longest line length is called
*max line* (*maxL*); it indicates the longest instance of being “stuck” in a
particular state together and is a measure of the stability of the system. 
The total *number of lines* on the plot (*NRLINE*) 
scales with structure: The more lines that exist, the more coupled the systems are. The
complexity or variability of line lengths is captured by a metric called
*entropy* (*ENTR*)---which may also be normalized by the total number of lines
(i.e., *normalized entropy*; *rENTR*)---and indicates
the stability and predictability of the system. When one of the signals gets
“stuck” in a state and the other moves on to other states, this results in
vertical line structures, which are quantified in *laminarity* (*LAM*;
i.e., the proportion of points forming vertical line structures) 
and trapping time (*TT*; i.e., the average length of the
vertical trajectories). For more detail on CRQA metrics, see @R-crqa.

@@

#### Metrics
Conducting WCRQA results in CRQA metrics (e.g., RR, DET, ENTR) for each
respective window. These metrics can then be plotted as a time series to
visualize their evolution over time. For these analyses, we decided to
focus on recurrence rate and determinism.

>>>>

The social cohesion calculation was performed on the tweet corpus
containing both English and Arabic tweets. All hashtags and URLs were included 
in the analysis.

@@

#### Metrics
While visual inspections can be informative, we can derive a variety of 
quantitative metrics from the cross-recurrence plot. Each of these metrics
provides information into the patterns and dynamics of the new shared system. 
These metrics are also critical for inferential
statistics. We will focus most directly on two of these metrics: 
*recurrence rate* and *determinism*.

@@

A number of other metrics provide insight not only into the amount of structure
between the systems but about the nature of this shared structure.
The average length of the line structures is called *mean line* (L), which can
be conceptualized as the average amount of time that the two time series move
together before one or both shift states. The longest line length is called
*max line* (*maxL*); it indicates the longest instance of being “stuck” in a
particular state together and is a measure of the stability of the system. 
The total *number of lines* on the plot (*NRLINE*) 
scales with structure: The more lines that exist, the more coupled the two 
systems are. The complexity or variability of line lengths is captured by a 
metric called *entropy* (*ENTR*)---which may also be normalized by the total 
number of lines (i.e., *normalized entropy*; *rENTR*)---and indicates
the stability and predictability of the system. When one of the signals gets
“stuck” in a state and the other moves on to other states, this results in
vertical line structures, which are quantified in *laminarity* (*LAM*;
i.e., the proportion of points forming vertical line structures) 
and *trapping time* (*TT*; i.e., the average length of the
vertical trajectories). For more detail on CRQA metrics, see @R-crqa.

@@

#### Metrics
Conducting WCRQA results in CRQA metrics (e.g., RR, DET, ENTR) for each
respective window. For these analyses, we decided to focus on recurrence rate 
and determinism.

### 2020-06-01 manuscript.tex
Edits to methods

While visual inspections can be informative, we can derive a variety of
quantitative metrics from the cross-recurrence plot. Each of these metrics
provides information into the pattern and dynamics of the new shared system
between the original time series. These metrics are also critical for inferential
statistics. We will focus most directly on two of these metrics:
\emph{recurrence rate} and \emph{determinism}.

@@

A number of other metrics provide insight not only into the amount of structure
between the systems but about the nature of this shared structure.
The average length of the line structures is called \emph{mean line} (L), which can
be conceptualized as the average amount of time that the two time series move
together before one or both shift states. The longest line length is called
\emph{max line} (\emph{maxL}); it indicates the longest instance of being \enquote{stuck} in a
particular state together and is a measure of the stability of the system.
The total \emph{number of lines} on the plot (\emph{NRLINE})
scales with structure: The more lines that exist, the more coupled the systems are. The
complexity or variability of line lengths is captured by a metric called
\emph{entropy} (\emph{ENTR})---which may also be normalized by the total number of lines
(i.e., \emph{normalized entropy}; \emph{rENTR})---and indicates
the stability and predictability of the system. When one of the signals gets
\enquote{stuck} in a state and the other moves on to other states, this results in
vertical line structures, which are quantified in \emph{laminarity} (\emph{LAM};
i.e., the proportion of points forming vertical line structures)
and trapping time (\emph{TT}; i.e., the average length of the
vertical trajectories). For more detail on CRQA metrics, see Coco and Dale (2018).

@@

Conducting WCRQA results in CRQA metrics (e.g., RR, DET, ENTR) for each
respective window. These metrics can then be plotted as a time series to
visualize their evolution over time. For these analyses, we decided to
focus on recurrence rate and determinism.

>>>>

While visual inspections can be informative, we can derive a variety of
quantitative metrics from the cross-recurrence plot. Each of these metrics
provides information into the patterns and dynamics of the new shared system.
These metrics are also critical for inferential
statistics. We will focus most directly on two of these metrics:
\emph{recurrence rate} and \emph{determinism}.

@@

A number of other metrics provide insight not only into the amount of structure
between the systems but about the nature of this shared structure.
The average length of the line structures is called \emph{mean line} (L), which can
be conceptualized as the average amount of time that the two time series move
together before one or both shift states. The longest line length is called
\emph{max line} (\emph{maxL}); it indicates the longest instance of being \enquote{stuck} in a
particular state together and is a measure of the stability of the system.
The total \emph{number of lines} on the plot (\emph{NRLINE})
scales with structure: The more lines that exist, the more coupled the two
systems are. The complexity or variability of line lengths is captured by a
metric called \emph{entropy} (\emph{ENTR})---which may also be normalized by the total
number of lines (i.e., \emph{normalized entropy}; \emph{rENTR})---and indicates
the stability and predictability of the system. When one of the signals gets
\enquote{stuck} in a state and the other moves on to other states, this results in
vertical line structures, which are quantified in \emph{laminarity} (\emph{LAM};
i.e., the proportion of points forming vertical line structures)
and \emph{trapping time} (\emph{TT}; i.e., the average length of the
vertical trajectories). For more detail on CRQA metrics, see Coco and Dale (2018).

@@

Conducting WCRQA results in CRQA metrics (e.g., RR, DET, ENTR) for each
respective window. For these analyses, we decided to focus on recurrence rate
and determinism.
